---
title: "DataExploration"
author: "Vanessa Whitehead"
date: "2024-04-16"
output: html_document
---
```{r include=FALSE}
library(shinycustomloader)
library(leaflet)
library(shiny)
library(shinythemes)
library(shinydashboard)
library(shinyWidgets)
library(bslib)
library(knitr)
library(tidyverse)
library(plotly)
library(readxl)
library(mapview)
library(ggplot2)
library(sp)
library(gstat)
library(RMySQL)
library(plainview)
library(readr)
```

This map shows the estimated monthly costs for each college town. These estimates are based on inputs for mpg and miles driven entered on the first page. 

## More Analysis

Besides the map above, the graphs on this page will **not** be based on input selected on the front page. 

**The Variables**

- **Rent**: webscrapped from Appartments.com
- **Gas Costs**:  webscrapped from GasBuddy.com
- **Mpg**: we will use ___. This is based on the average mile per gallon [citation]. 
- **Miles driven**: We are also using the estimated value __ for miles driven. [citation]
- **Maintenance costs**: are based on average maintenance costs from 
- 


```{r loadData, include=FALSE}
university_data <- read_csv("https://raw.githubusercontent.com/ArgentCode/DS401COLCalculator/main/universities.csv", show_col_types = FALSE) %>% 
  select(pretty_name, 
         zip, 
         appartment_mean_cost, 
         Appartment_Min, 
         Appartment_Max, 
         Monthly_food, 
         Car_Maintenance, 
         Gas, 
         uni_lat,
         uni_long,
         University,
         undergrad_pop, 
         city_pop,
         Car_Maintenance)
```

```{r cars}
head(university_data)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
