---
title: "DataExploration"
author: "Vanessa Whitehead"
date: "2024-04-16"
output: html_document
---

This map shows the estimated monthly costs for each college town. These estimates are based on inputs for mpg and miles driven entered on the first page. 

## More Analysis

Besides the map above, the graphs on this page will **not** be based on input selected on the front page. 

**The Variables**

- **Rent**: webscrapped from Appartments.com
- **Gas Costs**:  webscrapped from GasBuddy.com
- **Mpg**: we will use ___. This is based on the average mile per gallon [citation]. 
- **Miles driven**: We are also using the estimated value __ for miles driven. [citation]
- **Maintenance costs**: are based on average maintenance costs from 
- 


```{r include=FALSE}
library(readr)
library(dplyr)

university_data <- read_csv("https://raw.githubusercontent.com/ArgentCode/DS401COLCalculator/main/universities.csv", show_col_types = FALSE) %>% 
  select(pretty_name, 
         appartment_mean_cost, Appartment_Min, Appartment_Max, 
         Monthly_food, 
         Car_Maintenance, Gas, 
         uni_lat, uni_long, zip,
         University,
         undergrad_pop, city_pop
         )
```

```{r cars}
head(university_data)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
